Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.

### 2013-03-01 paper_dev/old.article.tex
201303_Mar01

%\documentclass[a4paper,10pt]{article}
\documentclass[journal]{IEEEtran}
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

@@

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin, 
	    Quang-Huy~Nguyen,
	    Chan-Hua~Vun%
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
}
\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun, are with School of Computer Engineering, 
Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
University of Science and Technology of China.
}% <-this % stops a space
\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS InnovationWorks Singapore for 
	initial discussions and for providing RADARSAT2 images used in this paper. }% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, Jul~2012}%
{ Le \MakeLowercase{\textit{et al.}}: Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters }

@@

\begin{abstract}

Logarithmic transformation has the potential to convert 
	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
	a simpler additive and homoskedastic distribution model.
From this homoskedastic model, within the log-transformed domain, 
	a few consistent measures of distance emerge.
With these, subtractive differences become consistent and predictable. 
We show, through experiments and analysis, that 
	the familiar mean squared error (MSE) criteria can reliably serve 
	as a single unifying performance indicator to evaluate SAR speckle filters. 
In homogeneous areas, we establish a mathematical relationship that links the variance of 
	log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
	is shown to be equivalent to the ratio-based radiometric preservation criteria that is usually assessed in the 
	original domain. 
Through experiments as well as analysis, we show that lower MSE suggests better feature detection and classification
	ability, which is an important requirement for subsequent post-filtering steps in practical SAR data processing.
In this paper, we hence propose and describe the combined use of log-transformed and MSE to evaluate SAR speckle 
	filters.

\end{abstract}

@@

The nature of SAR speckle is that
	it is stochastic even when the underlying radiometry is constant, 
	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluation of the estimators' performance. 
Estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance (hence lower MSE) indicating better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
In addition, due to the stochastic nature of SAR processing, as well as the simulating process, 
	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	prompting alternative evaluation criteria to be proposed.
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
	performance. 
As such, many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
Some papers do present quantitative measurements. 
However, due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The paper is structured as follows.
Section \ref{sec:lit_review} briefly surveys related work in the published literature, 
Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to 
	evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.

@@

%Addressing this issue, 
%There have been a few published articles dedicated to the topic of evaluating speckle filters.
%However, our survey of SAR speckle filtering research indicates 
%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
%In this section, we briefly review published work 
%	related to the topic of evaluating SAR speckle filters.	
It is customary to divide the performance evaluation of speckle filters across the two classes of 
	homogeneous and heterogeneous regions.
Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
	output (i.e. the speckle suppression power).
In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, 
	due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
	to be measured and compared.
%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
Furthermore, its application in a SAR processing framework should enable an improvement in the measurement, 
	detection or classification of the underlying radiometric features.
%As shown in the subsequent section, 
%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
	preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
	and variance error of the output.
As the MSE evaluation is a combined evaluation of bias and variance error, it is therefore capable of evaluating 
	the general requirements of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

For homogeneous scenes where the underlying radiometry is assumed to be constant, 
	the filtered results, statistically speaking, are considered to be samples of 
	a single but complex stochastic process.
%Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
	of speckle filters can be judged using the familiar bias and variance evaluation.
	%are expected to estimate with no radiometry bias. 
%The best filters achieve maximum speckle suppression power in such areas.

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent index for evaluation could be performed by a simple substraction.
In other words, it is clear that the bias evaluation in the log-transformed domain 
	can be used to similarily evaluate the radiometric preservation requirement of speckle filters.

Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we will also show that all of these standard filters 
	not only preserves the expected radiometric values in the log-transformed domain,
	they also preserve a number of subtractive and consistent measures of distance.

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the 
	log-transformed domain.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
	which is the primary criteria used to evaluate speckle filters over homogeneous area.
%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
%	which is a component of MSE evaluation, 
%	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.

Real-life and practical images, however, are not homogeneous.
Thus there are a number of associated difficulties in evaluating speckle filters over heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
	real-life images (hence, the need for speckle filters estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image 
	mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise (???? comprise of data with ?)
	the noise being removed (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluation, ratios that are smaller than unity are much 
harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, 
meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise 
would then resemble the familiar additive model, and the ratio image would then become a simple subtraction image.
The evaluation methodology for such a proposal does not change, 
	but now the residual image is additive and linear, 
	and would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).

Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied to extract features; examples of those that have been used are the 
	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
	and edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
of these methodologies.
This is because feature extraction algorithms are only approximations,
	whose accuracy is not only dependent upon the characteristics of the original image 
		but also heavily affected by 
		%reliant on 
		the inherent noise.
Unfortunately, speckle filters invariably alter the noise characteristics.
Thus, without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
	how to interpret the results, especially its accuracy.
%is just too imprecise for us.

Since SAR statistical models are quite well understood, 
	simulation experiments with known ground-truth can be employed 
		to evaluate speckle filters.
		%without the need to apply feature detection. 
In this paper, we also make use of a similar methodology discussed above with two important changes.
Firstly, our simulated experiments offer absolute ground-truth.
Secondly, our threshold-based feature extraction algorithm is extremely simple.
More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
This performance can be 
	conveniently visualised by plotting the Receiver Operating Characteristics Curve (ROC) 
	as well as objectively quantified by measuring the Area Under this Curve (AUC). 
As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
	feature preservation capabilities for different speckle filters.

@@

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
	normally at local or regional levels.
In fact, the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) 
	is likely to perform poorly in terms of preserving underlying radiometric differences 
	(such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

Overall, many different methods and metrics have been proposed to evaluate varios aspects of speckle filters. 
However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
	is still subjective in nature.

@@

Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, 
	the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, 
	which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. 
Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

@@

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss Markov theorem becomes applicable again, 
	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
Initial intitution (??? intuition?)
	suggests that each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is presented and discussed, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

@@

SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components,
	each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, 
	Leith_ProcIEEE_1971}. This interference can be considered as a random walk on the 2D complex plane 
	\cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, 
	height, distance and thus random phase of each elementary scaterer and its response.

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, the real part $A_r$ as well as 
the imaginary part $A_i$ of the observed SAR signal $A$ can then be considered as random variables from 
uncorrelated Gaussian distributed stochastic processes with zero means and 
% indentical ??? 
identical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

@@

\begin{table}[!h]
\caption{Both the mean and the variance of noisy SAR image data are related to the scale factor $\sigma$.}
\label{tbl:orginal_sar_avg_var}
\normalsize
\centering
%\begin{center}

@@

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic 
phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional 
expectation of the mean. 
In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; 
estimating variance is equal to estimating the mean and is equivalent to the main problem, 
ie. estimating the unknown parameter $\sigma$.

The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of look 
(ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both 
cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, 
which sets the stage for the discussion of logarithmic transformtion.

@@

In modelling, heteroskedasticity has direct consequences to the central question of homogeneity or heterogeneity. 
In normal images, the contrast or variance among neighboring pixels is often used to measure homogeneity. 
Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent 
to estimating $\sigma$).
%The fact give rise to the vicious circle in SAR speckle filtering.

@@

Case in point can be illustrated in the recently published improved sigma filter\cite{Lee_TGRS_2009}. 
The technique determines outlying points as being too far away from the standard deviation. 
However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required 
and used. It is interesting to note that the MMSE estimator used to estimate the mean 
in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.

>>>>

%\documentclass[a4paper,10pt]{article}
%ifdef FINAL
\documentclass[journal]{IEEEtran}
%endif
%ifdef REVIEW
\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
%endif
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

@@

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin, 
	Quang-Huy~Nguyen,
	Chan-Hua~Vun%
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun are with School of Computer Engineering, 
Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
University of Science and Technology of China.
}% <-this % stops a space
\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
{ Le \MakeLowercase{\textit{et al.}}: Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters }

@@

\begin{abstract}
Logarithmic transformation has the potential to convert 
	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
	a simpler additive and homoskedastic distribution model.
From this homoskedastic model, within the log-transformed domain, 
	a few consistent measures of distance emerge.
With these, subtractive differences become consistent and predictable. 
We show, through experiments and analysis, that 
	the familiar mean-squared-error (MSE) criteria can reliably serve 
	as a single unifying performance indicator to evaluate SAR speckle filters. 
In homogeneous areas, we establish a mathematical relationship that links the variance of 
	log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
For heterogeneous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
	is shown to be equivalent to the ratio-based radiometric preservation criteria, frequently employed in the 
	original domain. 
Through experiments as well as analysis, we show that lower MSE suggests better feature detection and classification
	ability, which can be an important requirement for subsequent post-filtering steps in practical SAR data processing.
Combining bias and variance evaluation, we propose and describe the use of MSE evaluation in log-transformed domain to evaluate SAR speckle 
	filters.
\end{abstract}

@@

The nature of SAR speckle is that
	it is stochastic even if the underlying radiometry is constant. 
And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
Estimators are typically evaluated based on the bias and variance properties of their estimates:
  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	prompting alternative evaluation criteria to be proposed.
In fact, our survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
	performance. 
As such, many papers lack a comparative basis beyond simple visual qualitative comparison on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, regrettably it lacks scientific objectivity. 
Some papers do present quantitative measurements. 
However, due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The paper is structured as follows.
Section \ref{sec:lit_review} briefly surveys related work in the published literature, 
Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to 
	evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.

@@

It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
	homogeneous and heterogeneous region evaluation.
Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
	output (a.k.a the speckle suppression power).
In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
	due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
	to be measured and compared.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
Furthermore, the application of any speckle filter in a SAR processing framework
   should enable an improvement in the measurement, 
	detection or classification of the underlying radiometric features.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
	preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
	and variance error of the output.
As the MSE evaluation is a combination of bias and variance error, it is therefore capable of evaluating 
	the general requirements of speckle filtering.

For homogeneous scenes where the underlying radiometry is assumed to be constant, 
	the filtered results are considered, statistically speaking, to be samples of 
	a single but complex stochastic process.
From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
	of speckle filters can be judged using the familiar bias and variance evaluation.

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent criteria for evaluation could be performed by a simple subtraction.
In other words, it is clear that the bias evaluation in the log-transformed domain 
	can be used to evaluate the radiometric preservation requirement of speckle filters.

Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we will also show that all of these standard filters preserve
	not only the expected radiometric values
	but also a number of subtractive and consistent measures of distance exhibited in the log-transformed domain.

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is mathematically related to variance in the 
	log-transformed domain.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
	which is the primary criteria used to evaluate speckle filters over homogeneous area.

Real-life and practical images, however, are not homogeneous.
Thus there are a number of associated difficulties in evaluating speckle filters over heterogeneous scenes.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparison. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
	real-life images.
And hence, the need for speckle filters estimation is warranted.

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise solely of
    the noise being removed (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
However, when displaying such images for visual evaluation, the ratios that are smaller than unity are much 
harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}. 
We therefore propose to adopt a log-transformed domain perspective 
  where the multiplicative noise would then be transformed into a more familiar additive model.
More importantly, the ratio image would then become a simple subtraction image.
The evaluation methodology for such adoption would not change. 
Only that the residual image would become linear and additive.
And thus it would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).

Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied to extract features; examples of those that have been used are the 
	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
	and edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
of these methodologies.
This is because feature extraction algorithms are only approximations,
	whose accuracy is not only dependent upon the characteristics of the original image 
		but also heavily affected by 
		the inherent noise.
Unfortunately, speckle filters invariably alter the noise characteristics.
Thus, without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
	how to interpret the results, especially its accuracy.

Since SAR statistical models are quite well understood, 
	simulation experiments with known ground-truth can be employed 
		to evaluate speckle filters.
In this paper, we also make use of a methodology similar to the ones discussed above with two important changes.
Firstly, our simulated experiments offer absolute ground-truth.
Secondly, our threshold-based feature extraction algorithm is extremely simple.
More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
This performance can be 
	conveniently visualized by plotting the Receiver Operating Characteristics Curve (ROC).   
It can also be objectively quantified by measuring the Area Under this Curve (AUC). 
As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
	feature preservation capabilities for different speckle filters.

@@

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogeneous scenes.
Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
	normally at local or regional levels.
In fact, the common consensus is that a powerful speckle suppression filter (for example the boxcar filter) 
	is likely to perform poorly in terms of preserving underlying radiometric differences 
	(e.g. causing excessive blurring).
Furthermore, we have not found many published articles combining the evaluation
  of these two seemingly contradicting requirements.

Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
	subjective in nature.

@@

Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
However since SAR data is heteroskedastic, which violates the assumptions of the Gauss-Markov theorem, 
	the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
  the ratio between the expected mean of the signal and the RMSE of the removed noise. 
The metric is argued to be similar in interpretation to the standard signal-to-noise ratio (SNR). 
Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

@@

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss-Markov theorem becomes applicable in this transformed domain, 
	the use of MSE is shown to be again relevant for evaluating statistical estimators (i.e. speckle filters).
Intuitively, each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is presented and discussed, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

@@

The SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components,
	each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, 
	Leith_ProcIEEE_1971}. This interference can be considered as a random walk on the 2D complex plane 
	\cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, 
	height, distance and thus random phase of each elementary scaterer and its response.

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, the real part $A_r$ as well as 
the imaginary part $A_i$ of the observed SAR signal $A$ can then be considered as random variables from 
uncorrelated Gaussian distributed stochastic processes with zero means and 
identical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

@@

\begin{table}[!h]
\caption{Both the mean and the variance of original SAR data are related to the scale factor $\sigma$.}
\label{tbl:orginal_sar_avg_var}
\normalsize
\centering
%\begin{center}

@@

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic 
phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional 
expectation of the mean. 
In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle: 
estimating variance is equal to estimating the mean and to estimating the unknown parameter $\sigma$, 
i.e. the main problem.

The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of looks 
(ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both 
cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, 
which sets the stage for the discussion of logarithmic transformtion.

@@

In modelling, heteroskedasticity has direct consequences to the central question of homogeneity or heterogeneity. 
In normal images, the contrast or variance among neighboring pixels is often used to measure homogeneity. 
Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
This makes the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent 
to estimating $\sigma$).
%The fact give rise to the vicious circle in SAR speckle filtering.

@@

A case in point is the recently improved sigma filter\cite{Lee_TGRS_2009}. 
The technique determines outlying points as being too far away from the standard deviation. 
However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required 
and used. It is interesting to note that the MMSE estimator used to estimate the mean 
in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.

Last, but certainly not least is the bad impact of heteroskedastic on SAR image interpretation. 
Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, 
target segmentation and/or target classification. 
Each of these tasks require good similarity or discriminant functions. 
Fundamental to these is the need of a consistent measures of distance. 
Unfortunately, by definition, heteroskedasticity leads to inconsistent measures of distance. 
This inconsistent measure of distance, coupled with the failure of the ordinary least square regression methods, are
 believed to cause a large class of artificial neural networks as well as a number of other computational 
 intelligence methods for SAR classification to underperform.
